Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-07-07 analysis/paper/paper.Rmd
Remove "final thoughts" and add paragraph on implementing layers

## Final Thoughts

>>>>

These layers provide increasing openness and reproducibility so Layer 1 should not be viewed as the starting point before moving on to Layer 2 and then Layer 3.
Rather the layers are provided to give the reader some idea of how much benefit end-users of the computational materials and data will derive at the expense of the increasing complexity.
Authors need not start with Level 1 before moving to Level 2 and then Level 3.
If they have the ability to start with depositing the computational materials and data and generating DOIs all parties will benefit from it.
However, we recognise that these steps may not be appropriate or attractive for various reasons and so have detailed other layers that improve openness and reproducibility.
